25-Figure3-051821

### 2021-09-11 notebooks/03-Fig3abde_4acd-051821.Rmd
fixed sensor plots to include non-go enriched for 0.2

# Load packages
```{r message=FALSE, warning=FALSE}
#library(tidyverse)
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- col[2:6] # brewer.pal(n = 6, name = "Set1")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

@@

## B
```{r}
sensor_connectivity_plot <-
  ggplot() +
  geom_density(data = sensor_connectivity_df %>% filter(type != "real"), aes(x = ratio, color = type)) +
  geom_vline(data = sensor_connectivity_df %>% filter(type == "real"), aes(xintercept = ratio, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("% of between group edges\nto all edges") +
  theme_bw() +
  scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
  theme(legend.position = "bottom") +
  scale_y_continuous(expand = c(0, 0))
  sensor_connectivity_plot
```

## D
```{r}
#sensors_pcc %>% drop_na()%>%kruskal.test(deg~go_group,data=.)

sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
sens_deg_comp <- ggplot(sensors_pcc %>% drop_na() %>% right_join(pcc_df)%>% mutate(go_group = factor(replace_na(as.character(go_group),"Non-sensor genes")),go_group=fct_reorder(go_group, sens),go_group=fct_relevel(go_group,'Non-sensor genes',after=Inf)), aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(
    outlier.shape=NA) +
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:5],'black')) +
  #ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
    axis.text.x = element_blank(), legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
sens_deg_comp

@@

## E
```{r}

if(nrow(sensors_pcc%>%drop_na(go_group))!=0){
sens_sens_comp <- ggplot(sensors_pcc %>% drop_na() %>% #mutate(go_group = fct_reorder(go_group, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = go_group, y = sens_norm, fill = go_group)) +
  geom_boxplot() +
#   geom_signif(
#     comparisons = list(
#       c("Hexose metabolic process", "Phenylalanine transport"), c("Tricarboxylic acid cycle", "Phenylalanine transport")#,
#       #c("phenylalanine\ntransport", "protein folding")
#     ),
#     annotation = c("*", "*"), y_position = c(0.007, 0.0075)#, 0.008)
#   ) +
  xlab("") +
  ylab("Sensitivity (a.u.)") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(),
        legend.title = element_blank())+
        ylim(NA, 0.008)

@@

effector_pcc %>% right_join(pcc_df)

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot+theme(legend.position='none'),width=3,height=3)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3,height=3)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3,height=3)

>>>>

# Load packages
```{r message=FALSE, warning=FALSE}
#library(tidyverse)
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- brewer.pal(n = 12, name = "Set3")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

@@

## B
```{r}
sensor_connectivity_plot <-
  ggplot() +
  geom_density(data = sensor_connectivity_df %>% filter(type != "real"), aes(x = ratio, color = type)) +
  geom_vline(data = sensor_connectivity_df %>% filter(type == "real"), aes(xintercept = ratio, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("% of between group edges\nto all edges") +
  theme_bw() +
  scale_color_discrete(labels = c("Random sampled set", "Sensors")) +
  theme(legend.position = "right") +
  scale_y_continuous(expand = c(0, 0))
  sensor_connectivity_plot
```

## D
```{r}
# sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)%>%fct_recode(
#   `Iron ion transport`  = "cellular response to iron ion starvation",
#   `Mitochondria nucleus\nsignaling pathway\nand\nTricarboxylic acid cycle`="mitochondria-nucleus signaling pathway",
#   `Phenylalanine transport`="phenylalanine transport",
#   `Hexose metabolic process`="hexose metabolic process",
#   `Tricarboxylic acid cycle`="tricarboxylic acid cycle"
# )

# sensors_sens_pval <- FSA::dunnTest(sens ~ go_group, sensors_pcc)
# sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
```

```{r}
sensors_pcc<- sensors_pcc%>%
    mutate(sensor_cluster=factor(replace_na(as.character(sensor_cluster),"Unclustered")),
    sensor_cluster = fct_reorder(sensor_cluster, sens))%>%
    group_by(sensor_cluster)%>%
    mutate(gid = cur_group_id())%>%ungroup()%>%
    mutate(cluster_or_go = ifelse(sensor_cluster=='Unclustered','Unclustered',
                                  ifelse(is.na(as.character(go_group)), gid, as.character(go_group))))%>%
    mutate(cluster_or_go = fct_recode(as.factor(cluster_or_go), `Iron ion\ntransport`  = "cellular response to iron ion starvation",
`Mitochondria nucleus\nsignaling pathway`="mitochondria-nucleus signaling pathway",
`Phenylalanine\ntransport`="phenylalanine transport",
`Hexose metabolic\nprocess`="hexose metabolic process",
`Tricarboxylic acid\ncycle`="tricarboxylic acid cycle"))%>%
    mutate(label = as.factor(case_when(
        cluster_or_go == 'Unclustered' ~ 'Unclustered',
        is.na(as.numeric(as.character(cluster_or_go))) == FALSE ~ paste0('SC',(gid-1)),
        TRUE ~ paste0('SC',gid-1,'\n(',cluster_or_go,')')
    )))
```

```{r}
sensors_sens_pval <- FSA::dunnTest(sens ~ as.factor(label), sensors_pcc)
sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]
```

```{r}
sensors_pcc %>% drop_na()%>%kruskal.test(deg~label,data=.)

#sensors_pcc$go_group <- as.factor(sensors_pcc$go_group)
sens_deg_comp <- ggplot(sensors_pcc %>% right_join(pcc_df)%>% 
                        mutate(label = factor(replace_na(as.character(label),"Non-sensor genes")),
                               label=fct_reorder(label, sens),
                               label=fct_relevel(label,'Non-sensor genes',after=Inf)), 
                        aes(x = as.factor(label), y = deg, fill = as.factor(label))) +
  geom_boxplot(
    outlier.shape=NA) +
  xlab("") +
  ylab("Degree") +
  scale_fill_manual(values = c(sensor_colors[1:10],'black')) +
  ggpubr::stat_compare_means(method = "kruskal.test", label.x.npc = .3) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(), 
        legend.title = element_blank(),
    legend.text = element_text(margin = margin(t = 10, b = 10))
  )+scale_y_log10()
sens_deg_comp

@@

## E
```{r}
comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)]
```

```{r}
comparisons <- str_split(sensors_sens_pval$res[sensors_sens_pval$res$P.adj < 0.1, ]$Comparison,' - ',2)

if(nrow(sensors_pcc%>%drop_na(go_group))!=0){
sens_sens_comp <- ggplot(sensors_pcc %>% mutate(label = fct_reorder(label, sens)) %>%
  mutate(sens_norm = sens / 5183), aes(x = (label), y = sens_norm, fill =(label))) +
  geom_boxplot() +
  geom_signif(
    comparisons = comparisons[order(sapply(comparisons, function(x) x[1], simplify=TRUE), decreasing=TRUE)],
    annotation = c("***","*" , "*" ,  "***"), y_position = c(0.007, 0.005,0.0055, 0.0075)#, 0.008)
  ) +
  xlab("") +
  ylab("Sensitivity (a.u.)") +
  scale_fill_manual(values = sensor_colors) +
  theme_bw() +
  theme(
        axis.title.y=element_text(size=14),
        axis.text.y=element_text(size=10),
        axis.text.x = element_blank(),
        legend.title = element_blank())+
        ylim(NA, 0.008)

@@

#effector_pcc %>% right_join(pcc_df)

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3,height=3)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3,height=3)
